\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instructions}}

### 2019-11-15 Documentation/Replication_Instruction.tex
final submission

The specific versions we use are: \textsc{Stata} 12, \texttt{R} 3.5.3 (code name \textit{Great Truth}) and MATLAB R2016a. The readers may need to do some very minor syntax change if using other versions. None of our results should be affected though. We did test our code in other versions of the softwares to the best as we could. Below are two examples:
\begin{itemize}
    \item
    Due to limited backward compatibility of \textsc{Stata} and that the \code{foreign} package of \code{R} supports only \code{.dta} files saved by \textsc{Stata} up to Version 12, readers with more recent version of \textsc{Stata} would need to either modify in the \code{.do} file everywhere \code{.dta} files are read and written, or use alternative \code{R} package (for instance \code{readstata13}) to convert the data in \bcode{cpsc\_convert.R} and \bcode{cec\_convert.R}.
    \item
    The syntax for several routines was slightly changed in MATLAB R2014b. If vintage versions are used, the reader would get a complaint saying (here from R2014a)
\begin{verbatim}    
Error using optimoptions (line 105)
'OptimalityTolerance' is not an option for FSOLVE.
A list of options can be found on the FSOLVE documentation page.
\end{verbatim}
    The code would run through by simply fixing the syntax to R2014a version; namely, the keywords to two optimization option need to be changed to \code{TolFun} and \code{MaxIter}. The code will run through seamlessly.
\end{itemize}

>>>>

The specific versions we use are: \textsc{Stata} 12, \texttt{R} 3.5.3 (code name \textit{Great Truth}) and MATLAB R2016a. The readers may need to do some very minor syntax change if using other versions. None of our results should be affected though. We did test our code in other versions of the softwares to the best as we could. Below are two examples:
\begin{itemize}
    \item
    Due to limited backward compatibility of \textsc{Stata} and that the \code{foreign} package of \code{R} supports only \code{.dta} files saved by \textsc{Stata} up to Version 12, readers with more recent version of \textsc{Stata} would need to either modify in the \code{.do} file everywhere \code{.dta} files are read and written, or use alternative \code{R} package (for instance \code{readstata13}) to convert the data in \bcode{cpsc\_convert.R} and \bcode{cec\_convert.R}.
    \item
    The syntax for several routines was slightly changed in MATLAB R2014b. If vintage versions are used, the reader would get a complaint saying (here from R2014a for instance)
\begin{verbatim}    
Error using optimoptions (line 105)
'OptimalityTolerance' is not an option for FSOLVE.
A list of options can be found on the FSOLVE documentation page.
\end{verbatim}
    The code would run through by simply fixing the syntax to R2014a version; namely, the keywords to two optimization options need to be changed to \code{TolFun} and \code{MaxIter}. The code would then run through seamlessly.
\end{itemize}
